\chapter{Project Broader Impacts}
\label{ch:projectbroaderimpacts}

\section{Ethical Implications or Issues of the Project}
The robots used in this project are very versatile in their ability to perform various tasks. The robots have a face recognition system that allows them to follow the movements of a person they have detected. For this project, the NAO robots must recognize and perform actions in response to one another. If this recognition system does not prove to be consistent, it could take action against the wrong individual. In other instances, NAO robots are utilized in the fields of healthcare and education where they are specifically programmed to interact with people. This is where the consistency in recognition becomes a requirement. If this feature is not accurate, the NAO robots can pose a threat to the safety of those around them. \par 
To prevent the implications of risk and danger to the participants of this project, the IEEE Code of Ethics is being thoroughly observed and practiced. It is understood that failure to comply with this code could cause harm to students, halt the completion of the project, and ultimately stain the image of the institution. \par 


\section{Knowledge of Contemporary Issues}

One of the biggest contemporary issues this project faces is the ethics behind the robots and the Artificial intelligence behind them. AI that can learn complex tasks on its own with minimal training data is critical. With this we have to make sure AI does not erode human freedom \cite{crowe_2018}. Robots and AI grow increasingly every year as technology advances and trying to use them ethically is a challenge engineers face daily. Is it right for us to replace humans with robots on simple tasks which increases unemployment and the de-skilling of the workforce \cite{crowe_2018}? \par
\section{Lifelong Learning}
Jacob - From my experience of working with many different Python libraries prior to this project, I am able to apply that knowledge by learning an entirely new library and software in NAOqi and Choregraphe. I hope to continue learning new techniques and software to aid in my future career/studies. \par
	Zeph - I have two goals that I plan to accomplish with the help of this project. The first being to understand how robots can be programmed to assist the lives of people. Secondly, I wanted to learn how to be more proficient in working in groups. Prior to being an engineer, I never thought I would be working with robots, however, being a part of this project is an experience that will assist in any future endeavour in robotics. I have never worked on a project of this scale before but it has been a great experience for me. It has taught me that with good collaboration, the hardest of assignments become simplified. Working on this project will definitely assist me in my career and the job market. \par 
	Seth - With taking many Engineering classes at ODU, it has made me a better critical thinker and problem solver when it comes to new material such as working with the NAO Robots. I plan on using what I learn from this project to further my career with robots, artificial intelligence and autonomous vehicles as they are one of my favorite things to work on; it will also benefit me as I have to communicate with my group daily and use teamwork to complete tasks. This is a very common thing in the Engineering field, you are almost always in some type of small group working together to achieve a common goal. \par 
	Stephen- I have been working in Dr. Khan’s vision lab for over a year at this point in semantic segmentation of flooding research. In my major, I have been focusing on machine learning, data analysis, and computer vision. It is always nice to see applications of machine learning and computer vision beyond use in a pure academic setting. I have no doubt that this project will help broaden my knowledge of what is possible with machine learning and artificial intelligence. \par 


\section{Impact of Engineering Solutions in a Global, Economic, Environmental, and Societal Context}
\subsection{Global}
One very important tool the NAO robot has is its language barrier. The NAO robot can recognize up to 20 languages and also communicate with dialogue with the correct programming \cite{softbank}. This is an extremely important feature and with this feature it can connect with almost anyone around the world.\par

Growingly, NAO robots are being used to help children learn their primary language with a second language \cite{hodson_2015}. With more people becoming bilingual it will connect different cultures around the world with the help of a robot. One thing a robot has over a language teacher is consistency and reliability. Also, NAO robots can be specifically programmed for certain students with learning disabilities which can help guide and motivate them. The NAO robots can also be placed as a security system or an alarm which can be used globally; the possibilities are endless with its ability to recognize multiple languages. \par

\subsection{Economic}
It is quite easy to realize the economic impact of developing such a robot. A NAO robot programmed in this manner has the potential to supplant preexisting jobs in the workforce that relate to the caretaking of kids with autism. For example, kids with autism may require caretakers with specialized education that also require a salary. While, NAO robots are expensive (around \$10,000) this is not even close to the potential salary of one full time caretaker. Consequently, those organizations that employ NAO robots for autism intervention and caretaking instead of specialized employees could see reduced expenses and make them more efficient and productive \cite{Acemoglu2020RobotsAJ}. However, such caretakers with specialized skills will find themselves out of a job. This same trend can be found in other industries such as car manufacturing where robots replace skilled workers and the workers are now unemployed \cite{Acemoglu2020RobotsAJ}. \par

\subsection{Environmental}
The impact many forms of technology leave on the environment can be negative. The pollution of land and air that occurs from the disposal of chemicals affects more than just agricultural yield. The short and long term exposure to pollutants comes with adverse health effects ranging from infections to cancer. The disposal of batteries used to power a variety of machinery plays a big part in the pollution process due to how they are absorbed in the environment. The NAO robots’ use of a lithium-ion battery greatly reduces the amount of this adulteration. Lithium is not expected to bioaccumulate and its human and environmental toxicity are low \cite{ARAL2008349}. To add to that, lithium in certain doses can stimulate certain plants \cite{ARAL2008349}. Compared to other types of batteries, lithium is considered less toxic to the environment.\par

To reinforce the NAO robots’ innocuousness to the environment, it is important to state the versatility of the robots. NAO robots make use of tactile sensors. These are devices that gather information based on physical interactions that include touch, pressure, and force. These are a big element to what allows the NAO robots to function, however, the chemicals used in the creation of these sensors are in question of being harmful to the environment. PVDF (Polyvinylidene fluoride), ZnO (Zinc Oxide), PZT(Lead Zirconate Titanate) are some of the materials used in the production of these sensors. This is where the versatility of the NAO robots comes into play. Even though the sensors are important, the robots can operate without them. Using a measure of the Instantaneous Capture Point, it is possible to develop an equilibrium-based interaction technique that does not require force or vision sensors \cite{6907003}. The NAO robots are designed in a manner to not be hazardous to the environment.\par

\subsection{Societal}

In a societal context, robots are seeing increasing use in homes, work, and healthcare.  More specifically, in healthcare, NAO robots can be used to simulate an Autism intervention, where one robot can be the child and another could be the parent.  Eventually, this could lead to using the NAO bot as the “parent” and performing an intervention with a human child.  There is currently evidence of other robots created by Softbanks Robotics being used in elder care homes, where the elderly interact with a robot instead of staff.  In this case, the robot being used is called Pepper, a 4 foot tall robot that is built to interact with residents, as opposed to just carrying out manual tasks \cite{lucy}.\par

As stated before, the use of NAO robots is popular in aiding children with Autism either in the classroom or at home; this will be made more popular through the use of mobile apps being developed to control the NAO robots \cite{7006084}.  Having an easily accessible software application for non-technical professionals, such as therapists and teachers, to use can increase the level of comfort in using the NAO robots, thus increasing human and robot relations and helping children with disabilities.\par

\subsection{Expected Overall Educational Benefits from this Project}

The overall study of the NAO robots greatly assists in the mastering of the Python API. The ability of the programming language to automate tasks, conduct data analysis, etc. is what makes it so useful. Due to this however, the language is very complex. It is quite in-depth in terms of syntax and can be difficult to produce results with if a user is not efficiently using it in its entirety. The programming of the NAO robots is a very thorough project which also implements the use of the Python language. The robots require well designed behavioral, recognition, and reinforcement modules to run properly. The completion of these will give the user a very extensive understanding of the language.\par